---
title: "Ex 01 - UN Votes"
author: "Mine Çetinkaya-Rundel"
output: 
  html_document: 
    highlight: pygments
---

```{r load-packages, include=FALSE}
library(unvotes)
library(tidyverse)
library(lubridate)
library(DT)
```

## Voting patterns in the UN General Assembly

The General Assembly is one of the six main organs of the United Nations, the only one in which all Member States have equal representation: one nation, one vote. At the General Assembly, Member States discuss, work together, and vote on a wide array of international issues covered by the UN Charter. These issues can be categorized into the following:

- Palestinian conflict
- Nuclear weapons and nuclear material
- Arms control and disarmament
- Human rights
- Colonialism
- Economic development

Let's take a look at the historic voting record of United States and one other 
country on these issues.

```{r plot-yearly-yes-issue, fig.width=10, warning=FALSE}
un_votes %>%
  dplyr::filter(country %in% c("United States of America", "Turkey")) %>%
  inner_join(un_roll_calls, by = "rcid") %>%
  inner_join(un_roll_call_issues, by = "rcid") %>%
  group_by(country, year = year(date), issue) %>%
  summarize(
    votes = n(),
    percent_yes = mean(vote == "yes")
    ) %>%
  dplyr::filter(votes > 5) %>%  # only use records with > 5 votes
  ggplot(mapping = aes(x = year, y = percent_yes, color = country)) +
    geom_point() +
    geom_smooth(method = "loess", se = FALSE) +
    facet_wrap(~ issue) +
    labs(
      title = "Percentage of 'Yes' votes in the UN General Assembly",
      subtitle = "1946 to 2015",
      y = "% Yes",
      x = "Year",
      color = "Country"
    )
```

## Exercises

1. How has the voting record of United States and Turkey changed over the years?
On which issues do these countries vote similarly, and on which issues do their 
votes differ? Discuss with your neighbor.
2. Update the code above to change `Turkey` to a different country of your 
choice. Knit this document to regenerate the plot, and discuss your new plot 
with your neighbor.

<br>

**Note:** You need to make sure you spell the name of the country of your 
choice the same way it's spelled in the dataset. You can use the table below 
to confirm spelling and capitalization.

```{r list-countries, echo = FALSE}
un_votes %>% 
  select(country) %>%
  arrange(country) %>% 
  distinct() %>%
  datatable(rownames = FALSE, options = list(dom = "ftp"))
```


## References

1. United Nations, Main Body, Main Organs, General Assembly. http://www.un.org/en/ga.
1. David Robinson (2017). unvotes: United Nations General Assembly Voting Data. 
R package version 0.2.0. https://CRAN.R-project.org/package=unvotes.
1. Erik Voeten "Data and Analyses of Voting in the UN General Assembly" 
Routledge Handbook of International Organization, edited by Bob Reinalda 
(published May 27, 2013).
