---
title: "Ex 02 - UN Votes Revisited"
author: "Mine Çetinkaya-Rundel"
output: 
  html_document: 
    highlight: pygments
---

```{r load-packages, include=FALSE}
library(unvotes)
library(tidyverse)
library(lubridate)
conflict_prefer("filter", "dplyr")
```

## Data prep for UN voting patterns plot

Earlier you used a dataset called `un_votes_joined` to build the plot on voting 
patterns on various issues in the UN General Assembly plot.

```{r un_votes_joined, warning=FALSE}
un_votes_joined <- un_votes %>%
  filter(country %in% c("United States of America", "Turkey")) %>%
  inner_join(un_roll_calls, by = "rcid") %>%
  inner_join(un_roll_call_issues, by = "rcid") %>%
  group_by(country, year = year(date), issue) %>%
  summarize(
    votes = n(),
    percent_yes = mean(vote == "yes")
    ) %>%
  filter(votes > 5)
```

The three data frames involved in the construction are the following:

- The `un_votes` dataset provides information on the voting history of the United Nations General Assembly. It contains one row for each country-vote pair.

```{r view-un_votes}
un_votes
```

- The `un_roll_calls` dataset contains information on each roll call vote of the United Nations General Assembly.

```{r view-un_roll_calls}
un_roll_calls
```

- The `un_roll_call_issues` dataset contains (topic) classifications of roll call votes of the United Nations General Assembly. Many votes had no topic, and some have more than one.

```{r view-un_roll_call_issues}
un_roll_call_issues
```

## Task

Work with your neighbir to describe what each line of the code for constructing `un_votes_joined` does. 

The following resources might be helpful for understanding the join functions:

  - [Cheatsheet for dplyr join functions
](https://stat545.com/bit001_dplyr-cheatsheet.html)
  - [Reference for join functions](https://dplyr.tidyverse.org/reference/join.html)

**Note:** LHS means left hand side, and RHS means right hand side.

**Hint:** Run the code one by one to view interim results, e.g.

```{r line1}
un_votes %>%
  filter(country %in% c("United States of America", "Turkey"))
```

```{r line2, warning=FALSE}
un_votes %>%
  filter(country %in% c("United States of America", "Turkey")) %>%
  inner_join(un_roll_calls, by = "rcid")
```

## References

1. David Robinson (2017). unvotes: United Nations General Assembly Voting Data. 
R package version 0.2.0. https://CRAN.R-project.org/package=unvotes.
1. Erik Voeten "Data and Analyses of Voting in the UN General Assembly" 
Routledge Handbook of International Organization, edited by Bob Reinalda 
(published May 27, 2013).
